A Methodology and Implementation of Automated Emissions Harmonization for Use in Integrated Assessment Models

### 2017-07-19 paper.tex
add detlef as author
clarify acknolwedments

The authors would like to acknowledge a number of colleagues who helped
contribute both discussion and feedback for this work, including Drs. Detlef van
Vuuren, Elmar Kriegler, Gunnar Luderer, and Joeri Rogelj. The authors further
with to thank \TODO{who?} for their generous funding of this effort.

>>>>

The authors would like to acknowledge a number of colleagues who helped
contribute both discussion and feedback for this work, including Drs. Elmar
Kriegler, Gunnar Luderer, and Joeri Rogelj. The authors further with to thank
the Global Environment Facility for their generous support. This project has
received funding from the European Union’s Horizon 2020 research and innovation
programme under grant agreement No 641816.
